Empirical Analysis of Performance Bottlenecks in Graph Neural Network Training and Inference with GPUs

### 2021-03-19 NEUROC/ms.tex
更新单位信息和致谢信息."

	\title{Empirical Analysis of Performance Bottlenecks in Graph Neural Network Training and Inference with GPUs}
    \author{Zhaokang Wang, Yunpan Wang, Chunfeng Yuan, Rong Gu$^*$ \corref{correspondingauthor1}, Yihua Huang$^*$ \corref{correspondingauthor2}}
    \cortext[correspondingauthor]{Corresponding authors with equal contribution}
    \ead{\{wangzhaokang, wangyp\}@smail.nju.edu.cn, \{cfyuan, gurong, yhuang\}@nju.edu.cn}
	\address{State Key Laboratory for Novel Software Technology, \\Department of Computer Science and Technology, Nanjing University, \\Nanjing 210023, China}

	\begin{abstract}
		The graph neural network (GNN) has become a popular research area for its state-of-the-art performance in many graph analysis tasks.
        %
		Recently, various graph neural network libraries have emerged.
        %
        They make the development of GNNs convenient, but their performance bottlenecks on large datasets are not well studied.
        %
		In this work, we analyze the performance bottlenecks in GNN training and inference with GPUs empirically.
        % 
		A GNN layer can be decomposed into two parts: the vertex and the edge calculation parts.
        %
		According to their computational complexity, we select four representative GNNs (GCN, GGNN, GAT, GaAN) for evaluation.
        % 
		We decompose their running time and memory usage, evaluate the effects of hyper-parameters and assess the efficiency of the sampling techniques.
        %
		The experimental evaluation indicates that the edge-related calculation is the performance bottleneck for most GNNs, dominating the training/inference time and memory usage.
        %
        The sampling techniques are essential for GNN training and inference on big graphs with GPUs, but their current implementation still has non-trivial overheads in sampling and data transferring.
	\end{abstract}

>>>>

	\title{Empirical Analysis of Performance Bottlenecks in Graph Neural Network Training and Inference with GPUs}
    \author{Zhaokang Wang, Yunpan Wang, Chunfeng Yuan, Rong Gu$^*$ \corref{correspondingauthor1}, Yihua Huang$^*$ \corref{correspondingauthor2}}
    \cortext[correspondingauthor]{Corresponding authors with equal contribution}
    \ead{\{wangzhaokang, wangyp\}@smail.nju.edu.cn, \{cfyuan, gurong, yhuang\}@nju.edu.cn}
	\address{State Key Laboratory for Novel Software Technology, Nanjing University, Nanjing 210023, China\\Department of Computer Science and Technology, Nanjing University, Nanjing 210023, China\\Collaborative Innovation Center of Novel Software Technology and Industrialization, Nanjing 210023, China}

	\begin{abstract}
		The graph neural network (GNN) has become a popular research area for its state-of-the-art performance in many graph analysis tasks.
        %
		Recently, various graph neural network libraries have emerged.
        %
        They make the development of GNNs convenient, but their performance bottlenecks on large datasets are not well studied.
        %
		In this work, we analyze the performance bottlenecks in GNN training and inference with GPUs empirically.
        % 
		A GNN layer can be decomposed into two parts: the vertex and the edge calculation parts.
        %
		According to their computational complexity, we select four representative GNNs (GCN, GGNN, GAT, GaAN) for evaluation.
        % 
		We decompose their running time and memory usage, evaluate the effects of hyper-parameters and assess the efficiency of the sampling techniques.
        %
		The experimental evaluation with PyTorch Geometric indicates that the edge-related calculation is the performance bottleneck for most GNNs, dominating the training/inference time and memory usage.
        %
        The sampling techniques are essential for GNN training and inference on big graphs with GPUs, but their current implementation still has non-trivial overheads in sampling and data transferring.
	\end{abstract}

### 2021-03-19 NEUROC/sec7-conclusion.tex
更新单位信息和致谢信息."

This work is funded in part by the National Key R\&D Program of China (2019YFC1711000), the China NSF Grants (No. U1811461, 62072230), the Collaborative Innovation Center of Novel Software Technology and Industrialization, Jiangsu, China, Alibaba Innovative Research Project, and the program B for outstanding PhD candidate of Nanjing University.

>>>>

This work is funded in part by the National Key R\&D Program of China [grant number 2019YFC1711000], National Natural Science Foundation of China [grant numbers U1811461, 62072230], Jiangsu Province Science and Technology Research Program [grant number BE2017155], Alibaba Innovative Research Project, and the Program B for outstanding PhD candidate of Nanjing University.
